%-------------------------
% Resume in Latex
% Author : Wilmer Gonzalez
% Based on: Sourabh Bajaj repo
% License : MIT
%------------------------

\documentclass[letterpaper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames, dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

% Page coloring, fonts, and logos
\usepackage{pagecolor}
\usepackage{lato}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{fontawesome}
% ---

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
% ---

% Sections formatting
\titleformat{\section}{ \vspace{1pt}\scshape\raggedright\large }{}{0em}{}[
  \color{black}
  \titlerule
  \vspace{-5pt}
]
% ---

% Custom commands

\newcommand{\sepsection}{\vspace{25pt}}

\newcommand{\resumeItem}[1]{%2
  \item\small{
    %\textbf{#1}
    #1
    %{: #2 \vspace{-2pt}}
  } }

\newcommand{\resumeSubheading}[4]{
  \vspace{8pt}
  \item%-1
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1}	  & #2		       \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}
  \vspace{-5pt}
}
\newcommand{\resumeSubSubheading}[2]{
  \vspace{1pt}
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}
  \vspace{-5pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}
  \vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
    \newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
    \newcommand{\resumeItemListEnd}{\end{itemize}
  \vspace{-5pt}}

\newcommand{\resumeTech}[2]{ \underline{#the 1:} #2 }

% COLOR THEMES SELECTION

% For Light theme un-comment this and comment on the Dark theme section below
\colorlet{textcolor}{black}
\colorlet{urlcolor}{blue}
\newcommand{\otherThemeRef}{\href{https://github.com/wilmeragsgh/resume/raw/master/wilmer_gonzalez_dark.pdf}{
    Dark
    \color{urlcolor}
    {\faicon{lightbulb-o}}}}
\newcommand{\latestVersion}{\href{https://github.com/wilmeragsgh/resume/raw/master/wilmer_gonzalez_light.pdf}{Latest
    \color{urlcolor}
    {\faicon{refresh}}}}

\begin{document}
% ---

% For the Dark theme un-comment this and comment on the Light theme section above
% \colorlet{textcolor}{white!80!gray}
% \colorlet{backgroundcolor}{black!30!gray}
% \colorlet{urlcolor}{blue!25!white}
% \AtBeginDocument{\color{textcolor}}
% \newcommand{\otherThemeRef}{\href{https://github.com/wilmeragsgh/resume/raw/master/wilmer_gonzalez_light.pdf}{Light \color{urlcolor}{\faicon{lightbulb-o}}}}
% \newcommand{\latestVersion}{\href{https://github.com/wilmeragsgh/resume/raw/master/wilmer_gonzalez_dark.pdf}{Latest \color{urlcolor}{\faicon{refresh}}}}

% \begin{document}
% \pagecolor{backgroundcolor}
% ---

% HEADING
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large NGUYEN DINH THI}
  \href{https://github.com/dinhthi12/portfolio}{\color{urlcolor} \faicon{link}}
  \\
  Backend developer
  &
  \href{https://mailto:thi884641@gmail.com}{\color{urlcolor}{\faicon{envelope}}
    \color{textcolor} thi884641@gmail.com} \\
  \textsl{Da Nang city}
  & {
      \color{urlcolor}{\faicon{phone}} \color{textcolor} 0796692773}
  \\
  \textsl{}
  &
  \href{https://github.com/dinhthi12}{ \color{urlcolor}{\faicon{github}}
    \color{textcolor} dinhthi12}		      \\
\end{tabular*}
% ---
\section{Summary}
\resumeSubHeadingListStart \resumeSubItem{{With 6 months of experience
      in software development, my goal is to become a bridge engineer, someone who
      connects departments and teams in projects to ensure information is effectively
      and seamlessly conveyed.}}

\resumeSubItem{{I aim not only to master the technical aspects but also
      to develop communication and project management skills to ensure the best
      integration and collaboration in the workplace.}}

\resumeSubHeadingListEnd

% EXPERIENCE
\section{Experiences}
\resumeSubHeadingListStart

\resumeSubheading {\href{}{Raven Games Corp}}{Company} {Backend
  developer}{11/2023 – 03/2024}
\resumeItemListStart \resumeItem{I efficiently configured Nginx to
  serve the Magento2 application while managing project source code using SVN.}
\resumeItem{Successfully deployed SSL certificates for enhanced
  security using ssl certificate and SSL certificate key files.}
\resumeItem{I leveraged PuTTY alongside SSH-RSA authentication on
  CentOS7 for remote administration tasks.}
\resumeItem{Available website:
{\href{https://ziu-shop.com/admin}{Ziushop.com}} }
\resumeItemListEnd \resumeTech{Technologies}{PHP, Slim framework,
  Magento2}\\
%   \resumeTech{Theory}{Machine learning, AutoML, Feature engineering, Project management.}
\vspace{3pt}
\resumeSubheading {\href{https://sun-asterisk.vn/}{Sun-asterisk
    (Internship)}}{Company}
{Backend developer}{04/2023 – 08/2023} \resumeItemListStart
\resumeItem{Contribute to building an effective Management Software Course
  Platform.}
\resumeItem{Enhanced teamwork proficiency by leveraging collaborative
  tools such as Slack and Git for seamless communication and efficient workflow
  management.}
\resumeItem{Participated in a professional project management life
  cycle, ensuring adherence to high standards and industry best practices.}
\resumeItem{Engaged in hands-on experiences with Ruby on Rails, gaining
  a deeper understanding of its capabilities and incorporating this knowledge
  into workplace workflows for more effective project development.}
\resumeItem{ Applied clean code techniques while tackling tasks.}
\resumeItemListEnd
%   \resumeTech{Theory}{Machine learning, AutoML, Feature engineering, Project management.}
\resumeSubHeadingListEnd

% ---
% PROJECTS
\section{Personal Projects}

\resumeSubHeadingListStart \resumeSubItem{{\textbf{Musical instrument
        system}}: This is an e-commerce website that integrates additional features
  including blogs, news about musical instruments, and consultation on courses
  musical.}

\begin{tabular}{|p{3.5cm}|p{15.3cm}|}
  \hline
  \multicolumn{1}{|c|}{\textbf{Role}}      &
  \begin{minipage}[t]{\linewidth}\begin{itemize}[leftmargin=*]\item[-] Leader

      \item[-] Back-end Developer\end{itemize}\end{minipage}
  \\
  \hline
  \multicolumn{1}{|c|}{\textbf{Team size}} & 2
  \\
  \hline
  \textbf{Responsibility}                  &
  \begin{minipage}[t]{\linewidth}\begin{itemize}[leftmargin=*]\item Compose
            comprehensive project documentation, encompassing implementation guides, user
            manuals, and source code documentation.

      \item Design database, develop and deploy critical functionalities utilizing
            the Laravel framework, with a focus on creating code that is not only
            maintainable and scalable but also optimized for performance.

      \item Handling tasks such as commits, pull requests, and branch management to
            uphold streamlined and efficient development
            workflows.\end{itemize}\end{minipage} \\
  \hline
  \textbf{Source code}                     &
  \textbf{\href{https://github.com/dinhthi12/musical_instrument_system}{Here}}
  \\
  \hline
  \textbf{Demo}                            &
  \textbf{\href{https://www.youtube.com/channel/UCK9nL1AikfpMvRTwed0NDxQ}{Here}}
  \\
  \hline
  \textbf{Technologies}                    & Laravel, blade, ajax,
  APIs                                                                       \\
  \hline
\end{tabular}

\resumeSubItem{{\textbf{CMS}}: A content management system (CMS) is a
  robust and user-friendly software platform specifically crafted to streamline
  the creation, organization, and publication of digital content on websites and
  web applications.}

\begin{itemize}[noitemsep,topsep=5pt,parsep=0pt,partopsep=0pt,
    leftmargin=-1pt]
  \vspace{3pt}

  \item {\textbf{Role}: Back-end Developer}
        \vspace{3pt}

  \item {\textbf{Team size}: 1}
        \vspace{3pt}

  \item {\textbf{Responsibility}}
        \begin{itemize}
          \item {\ Implemented an effective database
                design using Laravel migration, ensuring a systematic and organized structure
                for data storage and retrieval. }

          \item {\ Using the Laravel framework to build
                robust and scalable APIs, each tailored to specific project requirements. }
        \end{itemize}
        \vspace{1pt}

  \item {\textbf{Source code}: }
        \textbf{\href{https://github.com/dinhthi12/content-management-system}{\
            \color{urlcolor}
            {Here}}}
\end{itemize}
\resumeSubItem{{\textbf{Football fields management}}: Developing an
  application aimed at providing users with a straightforward interface to browse
  available soccer fields and make reservations based on their requirements.}

\begin{itemize}[noitemsep,topsep=5pt,parsep=0pt,partopsep=0pt,
    leftmargin=-1pt]
  \vspace{3pt}

  \item {\textbf{Role}: Back-end Developer}
        \vspace{3pt}

  \item {\textbf{Team size}: 3}
        \vspace{3pt}

  \item {\textbf{Responsibility}}
        \begin{itemize}
          \item {\ Develop and deploy the soccer field
                booking and online payment function, creating favorable conditions for users in
                the process of booking a field and completing payment. }

          \item {\ Adopt I18n function for multi-language
                support, helping to optimize user experience on cross-cultural platforms. }

          \item {\ Conducted thorough testing of
                functions and diligently addressed identified errors, ensuring the robustness
                and reliability of the system. }
        \end{itemize}
        \vspace{3pt}

  \item {\textbf{Source code}: }
        \textbf{\href{https://github.com/dinhthi12/ruby_oe_2023_football_fields_managerment}{\
            \color{urlcolor}
            {Here}}}
        \vspace{3pt}
\end{itemize}
\resumeSubHeadingListEnd
% ---
% EDUCATION
\section{Education}
\resumeSubHeadingListStart \resumeSubheading {FPT college}{09/2021 -
  10/2023}
{Majoring in software engineering}{Graduated} \resumeSubheading {Ha Noi
  Open University(HOU)}{03/2024 - Present}
{Majoring in software engineering}{} \resumeSubHeadingListEnd
% ---

% \hfill \textsl{ Click on items for details. \color{urlcolor}{\faicon{link}}}

% CERTIFICATIONS
\section{Certifications}

\resumeSubHeadingListStart \resumeSubItem{\textbf{HackerRank Coding}
  \textbf{\href{https://www.hackerrank.com/profile/thi884641}{\
      \color{urlcolor}{\faicon{link}}}} }

\resumeSubItem{\textbf{English} - Top Notch2}

\resumeSubItem{\textbf{JLPT} - N4}

\resumeSubHeadingListEnd

% ---
% PROGRAMMING SKILLS
\section{PROGRAMMING SKILLS}
\resumeSubHeadingListStart \resumeSubItem{\textbf{Operating system :}
  Ubuntu, CentOS7}

\resumeSubItem{\textbf{Languages :}Java, PHP, SQL, Javascript}

\resumeSubItem{\textbf{Frameworks :} Laravel, SLim}

\resumeSubItem{\textbf{Tools :} Draw.io, Trello, Postman, DBeaver}

\resumeSubHeadingListEnd

% ---
\end{document}
